---
title: "intro_to_basics"
output: html_document

--- type:MultipleChoiceChallenge key:167A4VcDii9Ku
## True basics

*** =assignment1
Which symbol marks the beginning of a comment in R?

*** =options1
- `%`
- `%*`
- [`#`]
- `@`
- `$`
- `*`
- `/*`


*** =assignment2
Which of the following is the recommended method of assigning a value to a variable?

*** =options2
- [`z <- 3`]
- `z is 3`
- `z gets 3`
- `z -> 3`
- `z == 3`


*** =assignment3
Which function is used to view the contents of your workspace?

*** =options3
- `show()`
- [`ls()`]
- `view()`
- `View()`
- `view_contents()`
- `show_workspace()`
- `view_workspace()`


--- type:BlanksChallenge key:167oSz8A19yBt
## Identify the class of an object

*** =pre_challenge_code
```{r}
library(purrr)
```

*** =code
```{r}
# use a purrr function!
{{_var1}}(1:3, ~ .x > 1)
```

*** =variables
var1:
  - 'map'
  - 'map_chr'
  - 'map_int'
  - 'map_lgl'

--- type:BlanksChallenge key:167UGAcPjWDNV
## Arithmetic operations - 2

*** =code
```{r}
team <- list(
    c(name = "Godel", country = "Austria"),
    c(name = "Escher", country = "Netherlands"),
    c(name = "Bach", country = "Germany")
    )

purrr::{{_func}}(team, {{_var1}})
```

*** =variables
var1:
  - '"country"'
  - '"name"'
  - '~ paste(.x, collapse = ",")'
func:
  - 'map'
  - 'map_chr'
