---
title: "intro_to_basics"
output: html_document

--- type:BlanksChallenge key:167oSz8A19yBt
## Basic mapping (1)

*** =pre_challenge_code
```{r}
library(purrr)
```

*** =code
```{r}
# use a purrr function!
{{_var1}}(1:3, ~ .x > 1)
```

*** =variables
var1:
  - 'map'
  - 'map_chr'
  - 'map_int'
  - 'map_lgl'

--- type:BlanksChallenge key:167UGAcPjWDNV
## Basic mapping (2)

*** =code
```{r}
team <- list(
    c(name = "Godel", country = "Austria"),
    c(name = "Escher", country = "Netherlands"),
    c(name = "Bach", country = "Germany"))

print(team)
purrr::{{_func}}(team, {{_var1}})
```

*** =variables
var1:
  - '"country"'
  - '"name"'
  - '~ paste(.x, collapse = ",")'
func:
  - 'map'
  - 'map_chr'

--- type:BlanksChallenge lang:r xp:100 skills:1 key:a12ac9df7b
## Basic mapping (3)

*** =pre_challenge_code
```{r}
library(purrr)
n <- 5
n_groups <- 3
distance <- rnorm(n*n_groups)
cost <- rnorm(n*n_groups, sd = rep(runif(n_groups, .5, 1.5), each = n))
tickets <- data.frame(distance, cost, group = rep(c('a', 'b', 'c'), each = n))
```

*** =code1
```{r}
str(tickets)

{{split_name}} <- split(tickets, tickets$group)

# fit linear model of cost ~ distance for each group
map({{split_name}}, {{_var1}})

```

*** =code2
```{r}
str(tickets)

{{split_name}} <- split(tickets, tickets$group)

# calculate the average cost for each group
map({{split_name}}, {{_var2}})
```

*** =code3
```{r}
str(tickets)

{{split_name}} <- split(tickets, tickets$group)

# calculate the max distance for each group
map({{split_name}}, {{_var3}})
```

*** =variables

split_name:
  - 'split_tickets'
  - 'splits'
  - 'group_tickets'
var1:
  - '~ lm(cost ~ distance, data = .x)'
var2:
  - '~ mean(.x$cost)'
var3:
  - '~ max(.x$distance)'


--- type:BlanksChallenge key:b68021f439
## Basic mapping (4)

*** =pre_challenge_code
```{r}
library(purrr)
```

*** =code
```{r}
{{dat_name}} <- list(
    c(name = "Godel", country = "Austria"),
    c(name = "Escher", country = "Netherlands"),
    c(name = "Bach", country = "Germany"))


{{dat_name}} %>% {{_func2}}({{_func}}({{dat_name}}, "name"))
```

*** =variables
dat_name:
  - 'team'
  - 'people'
  - 'present'
func:
  - 'map_chr'
  - 'map'
func2:
  - 'set_names'
